\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-08 ccs/eval.tex
minor

In Table~\ref{tab:nn}, 
the column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both the LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
%We note that while the \minion implementation is based on the ABY framework, it does not use the framework ``off-the-shelf'' and provide tailor-made optimizations for their applications. %By contrast, \tool focuses on generic
%2PC, exploiting ABY's performant implementation. Optimizations such as those found in \minion are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in \sectionref{pipeeval}.

@@

\subsection{Subsequent Work}
Subsequent to our work, Juvekar et al.~\cite{gazelle}  have
presented {\sc Gazelle}, a specialized protocol for DNNs.
{\sc Gazelle} use a lattice-based packed additively homomorphic
encryption scheme (PAHE) for arithmetic computations and garbled
circuits for boolean computations. {\sc Gazelle} can evaluate the CNN benchmark of
Table~\ref{tab:nn} in 0.8 seconds, as opposed to
5.1 seconds taken by \tool with the ABY backend. Such advances in
cryptographic backends are orthogonal to our contributions. In
particular, once {\sc Gazelle} is available, we could add it as another
cryptographic backend to \tool. Furthermore, the authors of Gazelle remark:
``A final, very interesting and ambitious line
of work would be to build a compiler that allows us to easily
express arbitrary computations and automatically factor the
computation into PAHE and two-party primitives'' -- the exact problem
that \tool solves.

>>>>

In Table~\ref{tab:nn}, 
the column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both the LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that while the \minion implementation is based on the ABY framework, it does not use ABY ``off-the-shelf'' and performs application-specific optimizations. In contrast, \tool focuses on generic
\mpc and directly exploits the exisiting performant implementations in ABY.
% Optimizations such as those found in \minion are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in \sectionref{pipeeval}.

@@

\subsection{Subsequent Work}
Subsequent to our work, Juvekar et al.~\cite{gazelle}  have
presented {\sc Gazelle}, a specialized protocol for DNNs.
{\sc Gazelle} use a lattice-based packed additively homomorphic
encryption scheme (PAHE) for arithmetic computations and garbled
circuits for boolean computations. {\sc Gazelle} can evaluate the CNN benchmark of
Table~\ref{tab:nn} in 0.8 seconds, as opposed to
5.1 seconds taken by \tool with the ABY backend. Such advances in
cryptographic backends are orthogonal to our contributions. In
particular, once {\sc Gazelle} is available, we could add it as another
cryptographic backend to \tool. Furthermore, the authors of {\sc Gazelle} remark:
``A final, very interesting and ambitious line
of work would be to build a compiler that allows us to easily
express arbitrary computations and automatically factor the
computation into PAHE and two-party primitives'' -- the exact problem
that \tool solves.

### 2018-05-08 ccs/related.tex
minor

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
This requires deep knowledge of cryptography
to ensure security.
Examples include classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, sequence analysis~\cite{franz}, biometric identification~\cite{huang}, matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees/forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.

>>>>

%\\\\
%\noindent\textbf{Custom \mpc protocols.} 
Many works have designed specialized protocols for various \mpc tasks. 
%The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. 
%This requires deep knowledge of cryptography
%to ensure security.
 Examples include ~\cite{barni,blanton,brickell,franz,huang,valeriaMatrix, valeriaRidge,shafindss,wu,secureml,minionn}.

%Examples include classification of medical ElectroCardioGram (ECG)~\cite{barni}, iris and fingerprint recognition~\cite{blanton}, remote diagnostics~\cite{brickell}, sequence analysis~\cite{franz}, biometric identification~\cite{huang}, matrix factorization and ridge-regression~\cite{valeriaMatrix, valeriaRidge}, machine-learning classification~\cite{shafindss}, decision trees/forests~\cite{wu}, neural network training~\cite{secureml} and prediction~\cite{minionn}.
